Optimal (Multiway) Spatial Joins

### 2024-05-29 msj.tex
yufei

Next, we prove the first bullet of statement (2), namely, $\bm{t}\in \J(R_1',...,R_{k-2}')$. Consider the $k$-tuple $(r_1,...,r_{k-2},h,v)\in \J_1$ given in statement (2). By definition of $\J_1$, segments $h$ and $v$ both cross each of the rectangles $r_1,..., r_{k-2}$. By the earlier discussion, $h$ and $v$ also both cross each of the trimmed rectangles $r_1',..., r_{k-2}'$. This means that the intersection of $h$ and $v$ must be a point in each of $r_1',..., r_{k-2}'$, suggesting $\bigcap_{i = 1}^{k-2}r_i' \neq \emptyset$. It thus holds that $\bm{t} = (r_1', ..., r_{k-2}')$ is a result tuple in $\J(R_1',...,R_{k-2}')$.

@@

Finally, we prove the second bullet of Statement (2). As we proved that $h$ and $v$ cross $r_i'$ for all $i \in [k-2]$, they must cross $\gbot(\bm{t})$ and $\gleft(\bm{t})$ as well. Hence, it suffices to show that both $h$ and $v$ cross $B_\bm{t}$. As proved in the last paragraph, the point $p = h \cap v$ is in $B_\bm{t}$. So, $h\cap B_\bm{t}$ and $v \cap B_\bm{t}$ are non-empty. Since $h$ (resp. $v$) crosses $r_i'$ for some $i \in [k-2]$, $r_i'$ does not cover any of the endpoints of $h$ (resp. $v$). Additonally, $B_\bm{t}$ is a subset of $r_i'$, so $B_\bm{t}$ does not cover any of the endpoints of $h$ or $v$. Therefore, $h$ and $v$ cross $B_\bm{t}$.

>>>>

We now prove the first bullet of statement (2), namely, $\bm{t}\in \J(R_1',...,R_{k-2}')$. Consider the $k$-tuple $(r_1,...,r_{k-2},h,v)\in \J_1$ given in statement (2). By definition of $\J_1$, segments $h$ and $v$ both cross each of the rectangles $r_1,..., r_{k-2}$. By the earlier discussion, $h$ and $v$ must also cross each of the trimmed rectangles $r_1',..., r_{k-2}'$. Hence, the intersection of $h$ and $v$ must be a point covered by each of $r_1',..., r_{k-2}'$, suggesting the point is in $\bigcap_{i = 1}^{k-2}r_i'$, which is thus not empty. Therefore, $\bm{t} = (r_1', ..., r_{k-2}')$ is a result tuple in $\J(R_1',...,R_{k-2}')$.

@@

Next, we prove the second bullet, namely, $h \in \dcross_H(\bm{t})$ and $v \in \dcross_H(\bm{t})$. It suffices to show only the former due to symmetry. To prove $h \in \dcross_H(\bm{t})$, we need to argue that $h$ crosses $\gbot(\bm{t})$ and $B_\bm{t}$. The first part, $h$ crossing $\gbot(\bm{t})$, is done because, as already explained, $h$ crosses each of $r_1', ..., r_{k-2}'$, and $\gbot(\bm{t})$ is one of those $k-2$ rectangles. To prove that $h$ crosses $B_\bm{t}$, first note that $B_\bm{t}$ (which is the intersection of $r_1', ..., r_{k-2}'$) is covered by $\gbot(\bm{t})$. From the fact that $h$ crosses $\gbot(\bm{t})$, we can assert that the y-range of $h$ contains that of $B_\bm{t}$. Hence, either $h$ is disjoint with $B_\bm{t}$ or $h$ crosses $B_\bm{t}$. However, $h$ cannot be disjoint with $B_\bm{t}$ because, as shown earlier, the intersection of $h$ and $v$ falls in $B_\bm{t}$. It thus follows that $h$ crosses $B_\bm{t}$.
